---
name: Tamás
surname: Nagy
position: "Assistant Professor"
address: "Institute of Psychololgy, Eötvös Loránd University"
phone: +36 30 627 6313
profilepic: "`r here::here('content/authors/admin/nt_cv_image.jpg')`"
www: nagytamas.netlify.app
email: nagytamas.hungary@gmail.com
twitter: nagyt
github: nthun
linkedin: tamas-nagy-phd-549bbb42
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "Tamás Nagy is an assistant professor of psychology at Eötvös Loránd University, Budapest. He has been teaching advanced research methodology, data analysis and statistical inference, and R programming for psychology students. He leads the ELTE Stress and Emotions Lab, which uses experimental methods and psychophysiology to uncover how we perceive physiological arousal, and how it affects our emotions, cognition, and behavior."
geometry: "top=0.75cm,top=0.75cm"
output: vitae::twentyseconds
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)  
library(tidyverse)
library(lubridate)
```

# Personal information  

Nationality: Hungarian  
Date of birth: 1st of July, 1981  
Address: 1147, Budapest, Fűrész utca 73B 1/4  

# Research interests

- The psychophysiology of human stress and emotions
- Machine learning, artificial intelligence, and computational science
- Improving psychological science

# Academic and industry positions

```{r}
tribble(
  ~ Position, ~Years, ~Institution, ~Where, ~Why, 
  "Assistant professor", "2017-", "Eötvös Loránd University, Institute of Psych.", "Budapest, Hungary", 
  c("Main activities: Teaching, research, supervising graduate and undergraduate students, leading Ph.D. projects, overseeing the faculty’s talent management program, managing grants, leading the Stress & Emotions Lab", 
    "Main achievements: reforming the 'Data Analysis and Statistical Inference' course for psychology undergraduates, establishing the R programming training for graduate students, creating a free online course for high school students called 'The Science of Psychology', winning and managing two research grants and four talent management grants, successfully increasing the number of students in the talent management program, open science"),

  "Lead researcher", "2014-2017", "Synetiq Ltd.", "Budapest, Hungary", 
  c("Main activities: Designing, managing, and analyzing neuromarkerting research projects at a startup company", 
    "Main achievements: Creating the research protocol involving psychophysiological methods and surveys. Leading successful research projects for large media and retail companies including HBO, AXN, RTL, BBC, The Dutch National TV, Lidl, Tesco, etc. Managed a research team to conduct media studies."), 

  "Research trainee", "2012–2013", "The University of Amsterdam", "Amsterdam, The Netherlands", "Main activities: Writing a manuscript on the effect of the acute stress response on alpha-amylase and cardiovascular indicators. PI: Dr. Jos Bosch", 
  "Research assistant", "2008-2010", "Hungarian Academy of Sciences", "Budapest, Hungary", "Main activities: Analyzing and planning of quantitative studies, preparing manuscripts in the Comparative Cross-cultural Psychology Lab", 

  "Counseling psychologist", "2006-2008", "Budapest University of Tech. and Econ.", "Budapest, Hungary", "Main activities: Psychological counseling for students, conducting psychological measurements"

)  |> 
  detailed_entries(Position, Years, Institution, Where, Why)
```


# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "Postdoctoral fellow", "2019-2023", "Eötvös Loránd University", "Budapest, Hungary",
  "Ph.D. studies in Psychology", "2010-2015", "Eötvös Loránd University", "Budapest, Hungary",
  "M.A. studies in Psychology", "2001-2006", "Eötvös Loránd University", "Budapest, Hungary"
)  |> 
  detailed_entries(Degree, Year, Institution, Where, .protect = TRUE)
```

# University offices and memberships



```{r}
tribble(
    ~ Year, ~ Position, 
    "2023-", "Member of the Institutional Research Ethics Board",
    "2022-", "Head of the Stress & Emotions Research Group",
    "2019-2021", "Acting head of the Social Interventions Research Group",
    "2019-", "Member of the Research Transparency Committee",
    "2018-", "Member of the ELTE Talent Management Council",
    "2018-", "Faculty head of the Scientific Student Circle of ELTE PPK"
    ) |> 
    brief_entries(Position, Year)
```


# Grants


```{r}
tribble(
    ~ Year, ~ Grant, ~ Details,
    "2018-2022", "National Talent Program", 
    c("Amount: HUF 10.4M", "Description: Short (1 year) grants to fund the faculty talent management program"),
    
    "2019-2023", "Postdoctoral grant", 
    c("Amount: HUF 25.5M", "Description: National Scientific Basic Research Programs - Research grant to study the role of emotional arousal in media-induced stress recovery"),
    
    "2018-2021", "Young researcher grant", 
    c("Amount: HUF 28.5M", "Description: National Scientific Basic Research Programs - Research grant to study the effects of intelligence mindset and mindfulness meditation on performance")
    ) |> 
    detailed_entries(what = Grant, when = Year, why = Details)

```

# Awards and honors


```{r}
tribble(
    ~ Year, ~ Grant, ~ Details,
    "2021", "ELTE Online course development award", "For creating e-learning material for 'Data analysis and Statistical Inference' course.",
    
    "2020", "ELTE's Promising Researcher Special Award for Open Science", "For outstanding achievements in the field of open science",
    
    "2018", "Erasmus+ research and training mobility", "Participation in a Bayesian statistics workshop in Amsterdam",
    
    "2016", "Special prize at the Brain and Vision Hackathon", "For integrating EEG systems into mobile, PC, and web applications",
    
    "2012-2013", "Erasmus+ traineeship", "University of Amsterdam, Netherlands",
    
    "2010-2014", "Hungarian state scholarship", "To pursue doctoral studies at ELTE"
    ) |> 
    detailed_entries(what = Grant, when = Year, why = Details)
```

# Teaching experience 

- Data analysis and statistical inference lecture (B.A., Hungarian)
- Multivariate statistics lecture (M.A., Hungarian and English)
- Statistical programming and data analysis in R seminar M.A. and Ph.D, English)
- Advanced research methodology in clinical and health psychology seminar (M.A., English)
- Advanced data analysis methods in R seminar (M.A., Hungarian and English)

# Workshops held
```{r}

tribble(
    ~ Year, ~ Title, ~With, ~ Details,
    "2022", "Regression Summer School 22", "University of Vienna", "Regression summer course jointly held of the students of ELTE and University of Vienna, https://osf.io/em5k4/",
    
    "2022", "Vienna Power Analyis in R Workshop", "University of Vienna", "Workshop about simulation based power analysis in R, https://osf.io/2tp3y/",

    "2022", "Introduction to R and the Tidyverse", "University of Vienna", "Two day introduction to R, https://osf.io/mx3vw/",
    
    "2022", "Meta-analysis Workshop", "Semmelweiss University", "Workshop about the theory and practice of meta-analysis (Hungarian), https://osf.io/ug8cz/",
    
    "2021", "Open Science Workshop", "Eötvös Loránd University", "Workshop about open science practices (Hungarian), https://osf.io/fz3pb/",
    
    "2020", "Open Science Workshop", "Eötvös Loránd University", "Workshop about open science practices (Hungarian), https://osf.io/swntk/",

) |> 
    detailed_entries(what = Title, when = Year, with = With, why = Details)
```

# Languages  

- English (professional level)
- Hungarian (native language)
- German (limited professional level)
- Japanese (basic level)

# Programming languages and data science tools  

- R: developer level
- git, markdown: professional level
- SQL, python, Matlab, latex: basic level (I can use them but prefer R and other tools whenever possible)
- SPSS, JASP, JAMOVI: professional level (I can teach these, and tutor others, but I don't use them myself)

# Journal positions and activity  

- Ad hoc peer review activity in multiple journals: https://www.webofscience.com/wos/author/record/J-5969-2019
- Associate editor at Hungarian Psychology Review (Magyar Pszichológiai Szemle) 

# Society memberships

- Hungarian Psychological Society
- Society for the Improvement of Psychological Science
- Member of the public body of Hungarian Academy of Sciences
- Member of the Psychological Science Accelerator

# Working papers and manuscripts under review

Hajdú, N., Szászi, B., Aczél, B., & Nagy, T. (Under review). Using supervised machine learning methods in psychological research. _Magyar Pszichológiai Szemle_. 

Nagy, T., Hergert, J., Rubínová, E., Tyson, G., Wallrich, L., Elsherif, M., Skvortsova, A., Payne, J., Alarie, S., Wang, Y. A., Graves, K., Schmidt, K., Sotola, L., Waltzer, T., Gjoneska, B., Seetahul, Y., Yang, Y.-F., Scharfenberg, D., & Moreau, D. (Under review). The Questionable Research Practice Bestiary. _Advances in Methods and Practices in Psychological Science_. 

Nagy, T., Ipacs, H., Ferentzi, E., & Köteles, F. (Under review). Heart rate perception and expectation impact laboratory-induced perceived stress. _Biological Psychology_.


# Peer reviewed journal articles and book chapters

```{r}

bibliography_entries(here::here("publications.bib")) |> 
  mutate(year = as_date(issued) |> year()) |>
  arrange(-year)
```
